%% FRONTMATTER
\begin{frontmatter}

% generate title
\maketitle

\begin{abstract}
Two searches for massive resonances decaying into qV/VV/VH final states are presented, in which V denotes W, Z bosons, and H denotes Higgs boson. 

The data analyzed corresponds to an integrated luminosity of 19.7~fb$^{-1}$ collected by the CMS detector in proton-proton collisions at $\sqrt{s}=8$~TeV.
The cutting edge jet substructure algorithms are used to distinguish V and H boson jets from the standard model QCD quark/gluon jets background.

Exclusion limits are set at a confidence level of 95\% on the production cross sections of: (i) excited quark resonances q* decaying to qW and qZ for masses less than 3.2 TeV and 2.9 TeV, respectively, (ii) a Randall--Sundrum graviton \GRS decaying into WW for masses below 1.2 TeV, and (iii) a heavy partner of the W boson ${\rm W'}$ decaying into WZ for masses less than 1.7 TeV. 
In HVT model scenario B, resonance masses are excluded for ${\rm W'}$ in the interval [1.0, 1.6] TeV, 
for ${\rm Z'}$ in the intervals [1.0, 1.1] and [1.3,1.5] TeV, and for mass-degenerate  ${\rm W'}$ 
and ${\rm Z'}$ in the interval [1.0, 1.7] TeV.
A model with a “bulk” graviton $\GBulk$ that decays into WW or ZZ bosons is also studied. 

\vspace{.3cm}
\noindent Primary Reader: Petar Maksimovic\\

\end{abstract}

\begin{acknowledgment}
I would like to thank my Ph.D advisor, Petar Maksimovic. 
He taught me how to accomplish a physics analysis. 
He taught me how to collaborate with people in a large organization. 
He taught me how to stay calm when bad things happen. 
He shared with me his life stories to help me survive in such a different culture. 
He is always so supportive and always happy to help. 
I would like to express my sincere gratitude for him being a brilliant advisor and a fantastic mentor. 


There are also many people to thank for my education in experimental particle physics, but probably 
none more than Andreas Hinzmann. I thank him for teaching me all the techniques and always being super patient in answering my questions. I thank him for being a wonderful leader and an excellent colleague. 

I would like to thank Professor Morris Swartz for helping me with analysis questions and 
for being my analysis committee and thesis committee. 

I would like to thank my colleagues and friends in the physics department. Thanks for Lei Feng and Can You for being wonderful officemates, discussing the analysis questions and sharing frustrations and happiness as being a physics Ph.D. 
Thanks for Guofan Hu for his helps in these years, and for being my student mentor for the first two years of my Ph.D life. Thanks for all the advices and suggestions. 
I would like to thank David Fehling, Kevin Nash, Marc Osherson, Ian Anderson, Chris Martin for helping me with specific analysis questions and for being great colleagues for all these years. 
I would like to thank my JHU friends, Longyu Zhao, Yuchong Shao, Kui Chen, Zhilei Xu, Bingxiao Xu, Yaofu Zhou, Jiajia Wen, Shan Wu, Danru Qu, Ting Su,  Liang Dai, Hongbin Chen and etc. 

I would like to thank my parents, for their love and care, for their support and understanding, for their patience and guidance. Last but not the least, I would like to thank my fiancee, Tian Mao, for her support and for sharing life and happiness with me. 
  

\end{acknowledgment}

%\begin{dedication} 

%\end{dedication}

% generate table of contents
\tableofcontents

% generate list of tables
\listoftables

% generate list of figures
\listoffigures

\end{frontmatter}
