\section{Results and conclusions}
\label{sec:conclusions}

Our limits results are summarized in Table~\ref{table:results}.

A data sample corresponding to an integrated luminosity of \intlumi
collected in pp collisions at $\sqrt{s}=8$\TeVcc with the CMS detector
has been used to measure the $\PW/\cPZ-$ and H-tagged dijet mass spectrum
using the two leading jets within the pseudorapidity range $|\eta| <
2.5$ and with pseudorapidity separation $|\Delta\eta| < 1.3$.  The QCD
background is suppressed using
 jet substructure tagging techniques and/or b-tagging,
which identify boosted bosons decaying into hadrons.  In particular, we
use the invariant mass of pruned jets and the $N$-subjettiness ratios
$\tau_{21}$ and $\tau_{42}$, as well as b tagging applied to the subjets
of the Higgs jet, to discriminate
against the initially overwhelming QCD background.  The remaining QCD
background is estimated from a fit to the parameterized shape.
We have searched for the signal as a peak on top of the smoothly
falling QCD background. Z' is excluded in resonance mass regions, [1.0, 1.1] and
[1.3, 1.5] TeV. While W' is excluded in resonance mass regions [1.0, 1.6] TeV.  
%Expected limits are set on Z' at 1.3TeV 
In HVT B model, W' and Z' are degenerate, so we combine them together. The exclusion limit
is set on [1.0, 2.1] TeV.

\begin{table}[htb]
\begin{center}
  \caption{Summary of observed limits on resonance masses at 95\% CL
    and their expected values, assuming a null
    hypothesis. The analysis is sensitive to resonances heavier than 1\TeVcc . \label{table:results}}
\begin{tabular}{ ccc}
\hline
Process      & Observed & Expected \\
& excluded mass limit (\TeVcc) & excluded mass limit (\TeVcc) \\
\hline
${\rm V' \to VH}$     & [1.0, 1.7], [1.9, 2.0]  & 2.0 \\
${\rm Z' \to HZ(qq)}$ & [1.0, 1.1], [1.3, 1.5] & 1.3 \\
${\rm W' \to HW(qq)}$ & [1.0, 1.6] & 1.7 \\
\hline
\end{tabular}
\end{center}
\end{table}



%No evidence has been found for new resonance production in the $\PW/\cPZ$-tagged dijet
%spectrum.  A 95\% CL lower limit is set on the mass of excited quark
%resonances decaying into qW (qZ) at 3.17 (2.88) TeV.  $G_{RS}$
%decaying into WW is excluded up to 1.24 TeV.  $\PWpr$
%decaying into WZ is excluded in the ranges $[1.00,  1.23]$,  $[1.39,  1.52]$ and $[1.57,  1.61]$ TeV.
